---
title: "Fatality Analysis Reporting System"
author: "Xiangming Ding"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Fatality Analysis Reporting System}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

FARS is a nationwide census providing NHTSA, Congress and the American public yearly data regarding fatal injuries suffered in motor vehicle traffic crashes.This package will provide some function to calculate the statistics of the accidents and to visulaize the location of the fatal accidents. 

### Make the file name

```{r}
#  make a filename from the year
make_filename <- function(year) {
  year <- as.integer(year)
  sprintf("accident_%d.csv.bz2", year)
}
make_filename(2015)
```

### Read a file
```{r}
fars_read <- function(filename) {
  filename <- system.file("extdata", filename, package="fars")
  if(!file.exists(filename))
    stop("file '", filename, "' does not exist")
  data <- suppressMessages({
    readr::read_csv(filename, progress = FALSE)
  })
  dplyr::tbl_df(data)
}
fars_read("accident_2015.csv.bz2")
```
### Read multiple files 
```{r}
library(magrittr)
fars_read_years <- function(years) {
  lapply(years, function(year) {
    file <- make_filename(year)
    tryCatch({
      dat <- fars_read(file)
      dplyr::mutate_(dat, year = year) %>%
        dplyr::select_("MONTH", "year")
    }, error = function(e) {
      warning("invalid year: ", year)
      return(NULL)
    })
  })
}
fars_read_years(c(2013,2014,2015))
```
### Summarize the number of accident in each year
```{r}
library(magrittr)
fars_summarize_years <- function(years) {
  dat_list <- fars_read_years(years)
  dplyr::bind_rows(dat_list) %>%
    dplyr::group_by_("year", "MONTH") %>%
    dplyr::summarize_(n = ~n()) %>%
    tidyr::spread_("year", "n")
}
fars_summarize_years(c(2013,2014,2015))
```
